Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-16 patient-clinician-workshop/pccworkshop.tex
table in margin
added label
More collection words:
pivot

\begin{table*}[htb]
\small
\begin{tabular}{p{5.0cm}  p{4cm} l}

 measurement & products & price range \\
\hline
general activity (walking/jogging) & FitBit, Nike FuelBand  & 49-199 \\ 
weight & Writhings WiFi Scale & 200 \\
blood pressure & Writhings BPM & 200 \\ 
sleep duration & Zeo Pro, WakeMate, & 100-300  \\
heart rate variability & Zensorium Tinke & 200 \\
blood oxygenation & Zensorium Tinke & 200 \\ 
respiratory rate & Zensorium Tinke & 200 \\ 
galvanic skin repsonse & BodyMedia CORE 2 &  50-100 \\
body temperature & BodyMedia CORE 2 &  50-100 \\ 
Eating & Hapifork & (not yet released) \\ 
\end{tabular}
\caption{\emph{Consumer-grade activity sensors}: Activity and physiological measurememnt sensors with automatic data uplink to cloud services }
\end{table*}

>>>>

\newpage

\marginpar{
\begin{table}
\small
\begin{tabular}{p{3cm}  p{6cm} p{1.5cm}}

product & measurement indices & price range (approx. USD) \\
\hline
FitBit & general activity (walking/jogging) & \$50 \\
Nike FuelBand & general activity (walking/jogging) & \$199 \\ 
Writhings WiFi Scale & weight & \$200 \\
Writhings BPM & blood pressure & \$200 \\ 
Zeo Pro & sleep duration \& quality & \$200 \\
WakeMate & sleep duration & \$50  \\
Zensorium Tinkne & heart rate variability, blood oxygenation, respiratory rate & \$200 \\
BodyMedia CORE 2 & galvanic skin repsonse, body temperature, sleep, respiratory rate, heart rate & \$50-100 \\
body temperature & BodyMedia CORE 2 &  (TBD) \\ 
Hapifork & eating time, rate, frequency & (TBD) \\ 
\end{tabular}
\caption{\emph{Consumer-grade activity sensors}: Activity and physiological measurememnt sensors with automatic data uplink to cloud services }
\label{sensors}
\end{table}
}
\vspace{6cm}
